Efficient Coalition Formation \\ for Web Services

### 2013-05-28 papers/coalition-journal-extension/coalition_journal.tex
Changes

>>>>

In this section, we present the web service and community coordinator's intractions, the task distribution process and revenue models in web service communities.

\subsection{Task destribution}

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well stablished market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterizd by a request rate $(R_M)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $T_{ws}$ is excluded. This exclusion allows us to build our analysis on the particular value of $T_{ws}$. Throughput is the average rate of tasks a web service can perform per time unit. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $T_{ws}$.
The community master uses a weighted fair queuing scheduling technique to distribute task ammoung its members.

\section{Web Service Cooperative Games}\label{s:model}
